---
title: "Title"
subtitle: "Subtitle"
author: "Author"
date: "Date"
output:
  xaringan::moon_reader:
    css: ["default", "assets/ude_fonts.css", "assets/ude.css"]
    self_contained: true # if true, fonts will be stored locally
    seal: true # show a title slide with YAML information
    includes:
      in_header: "assets/mathjax-equation-numbers.html"
    nature:
      beforeInit: ["assets/remark-zoom.js", "https://platform.twitter.com/widgets.js"]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9' #alternatives '16:9' or '4:3' or others e.g. 13:9
      navigation:
        scroll: TRUE #disable slide transitions by scrolling
---

```{r, load_refs, include = FALSE, echo=FALSE, cache=FALSE}
library(RefManageR)
BibOptions(check.entries = FALSE, 
           bib.style = "authoryear", 
           cite.style = 'authoryear', 
           style = "markdown",
           hyperlink = FALSE, 
           dashed = FALSE)
myBib <- ReadBib("assets/example.bib", check = FALSE)

# packages
source(here::here('00_packages/packages.R'))
```

# Installing 

These are slides made with the **xaringan** package which is on CRAN available, but I recommend installing the development release from `r icon::fa("github")`

```{r, eval = FALSE}
devtools::install_github('yihui/xaringan')
```

.pull-left[
You will also need two other CSS files for the custom University of Duisburg-Essen styling:

- `edu_fonts.css`
- `edu.css`
]
.pull-right[
If you want the University signet to show up on the title slide, you'll also need:

- `signet_ude_rgb_neg.png`
]

These are available in the assets folder of the GitHub code repository [`r icon::fa("github")` `jens-klenke/slides_xaringan`](https://github.com/jens-klenke/slides_xaringan/tree/main/01_slides/assets)

To make things easy to get started, I recommend downloading a copy of the `slides_xaringan` repo [`r icon::fa("file-archive")`](https://github.com/jens-klenke/slides_xaringan/archive/main.zip) and make changes to the slides. 


---
# xaringan 

- Press `h` or `?` to see the possible ninjutsu you can use in remark.js.

- You can see all the goodies like this (hint press `p`).

- Check out more in-depth tutorial [here](https://slides.yihui.name/xaringan/#1)


---
## Why xaringan/remark.js? `r icon::fa("check-circle", pull = "right")`

- Printing (in Google Chrome) is a lot more reliable for xaringan/remark.js
- The customisation of the CSS and using it is a lot easier in xaringan/remark.js
- You almost never need to write any manual HTML chunks (e.g. `<div style="text-align: center;"></div>`)
- With remark.js' Markdown, you can add arbitrary CSS classes to elements using syntax `.className[elements]`, which is very handy compared to `<span class="className"></span>`
- You can write slide notes under three question marks `???`. These notes are only displayed in the presentation mode, and only the speaker can see these notes. 
- The keyboard shortcuts: press keys like `P` (presentation mode), `C` (clone slides to a new window, useful for presentation mode), `B` (black out), `M` (mirror the slide), and `H` (help), etc.

More: [yihui.name/en/2017/08/why-xaringan-remark-js/](https://yihui.name/en/2017/08/why-xaringan-remark-js/)

---

# Scrolling R output

If you just want a section of the output to be scrollable (not the whole page).  You need to define how many lines you want the "box" to show.  There are classes for `.scroll-box-8[]` for 8 lines, `.scroll-box-10[]` for 10 lines, ... , `.scroll-box-20[]` for 20 lines.

### Example

`.scroll-box-8[]` 

.scroll-box-8[
```{r}
swiss[,1:3]
```
]

.pull-down[
Customized scroll boxes must be first implemented in the `edu.css` file.
]
---
# googleVis

Embedded by exporting to HTML and including as an iframe.

```{r gvisMergeExample, results='asis', echo=FALSE, message=FALSE}
library(googleVis)
Geo <- gvisGeoChart(Exports, locationvar='Country', colorvar='Profit') 
cat(Geo$html$chart, file="Geo.html")
```
<iframe src = "Geo.html" width = "100%" height = "90%" frameborder="0"></iframe>


---

## Content boxes `r icon::fa("box", pull = "right")`

.content-box-blue[This is a `.content-box-blue[]` chunk.

]

--

If you have just a few words, it only highlights the words:


.content-box-army[`.content-box-army[]`] .content-box-yellow[`.content-box-yellow[]`]

.content-box-red[`.content-box-red[]`] .content-box-purple[`.content-box-purple[]`]

--

If the text includes a new line character, you get a 100% width box.  I've used `.columns-2[]` it's 100% of the column width.

.columns-2[
.content-box-gray[
`.content-box-gray[]`
]
.content-box-green[
`.content-box-green[]`
]
]

---

## Quotes `r icon::fa("quote-right", pull = "right")`

.small[
We can include **block quotes** using<br>
`<blockquote>Quote goes here</blockquote>` 

or<br>
`> Quote goes here`

or `.blockquote[Quote here]`
]
.pull-left[

<blockquote>
Statistics is the grammar of science. 
.right[-- <cite>Karl Pearson</cite>]
</blockquote>

.blockquote[Quote]

> Quote quote  
]



.pull-right[.small[
```
<blockquote>
Statistics is the grammar of science. 
.right[-- <cite>Karl Pearson</cite>]
</blockquote>



.blockquote[Quote]



> Quote quote
```

]]




